---
output:
  md_document:
    variant: markdown_github
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

# kagari (縢り)

This package organizes individual data from various measuring instruments into tidy dataset.
`kagari` is a Japanese word meaning sew (c.f [和綴じ](https://www.google.co.jp/search?q=%E5%92%8C%E7%B6%B4%E3%81%98&source=lnms&tbm=isch)).
The author hope to sew a user-friendly book---i.e. tidy dataset---from individual pages---i.e. messy raw data.

You can install:

* the latest development version from github with

```R
# install.packages("devtools") # if not installed
devtools::install_github("KeachMurakami/kagari")
```

## Prerequisite

```{r prerequisite}
library(tidyverse)
library(kagari)
```

## Data load

`read_***` deals with raw data obtained by `***`---a name of the software or the device:

* `read_li6400()`: reads `.txt`/`.csv`/`.tsv` format data obtained by LI6400/LI6400XT (LI-COR) with Xterm.

* `read_junior_pam()`: reads `.csv` format data obtained by JUNIOR-PAM (Heinz Walz) with WinControl.

* `read_field_lambda()`: reads `.csv` format data obtained by field-lambda with color viewer.

* `read_color_reader()`: reads `.csv` format data obtained by CR-10 Plus (Konica Minolta).

The first argument is always a file path.
The output is wide format data containing the measured variables and measured times.

## Data manipulation

`mutate_***` calculates parameters from raw data obtained by `***`---a name of the software or the device---and adds new columns to the input `tibble`.

* `mutate_oxy()`: calculates and adds maximum gross photosynthetic O~2~ evolution rate, functional PSII content, and cytochrome content from data obtained by liquid phase oxygen electrode system (Hansatech) with single-turnover.

```{r demo-mutate_oxy}
tibble(o2_calibration = c(1.3, 1.31),
       pn_under_saturing_irradiance = c(.3, .51),
       pn_under_dark = c(-.11, -.05),
       pn_under_fr_and_flash = c(.1, .09),
       pn_under_fr = c(-.002, 0)) %>%
  mutate_oxy(.tbl = ., calb = o2_calibration,
             positive_pmax = pn_under_saturing_irradiance, negative_pmax = pn_under_dark,
             positive_psii = pn_under_fr_and_flash, negative_psii = pn_under_fr,
             leaf_area = 2.22*10^-4, hz = 10) %>%
  knitr::kable(format = "markdown")
```

The first argument is always a tibble.

## Session information

```{r sessioninfo}
devtools::session_info()
```
