---
output:
  md_document:
    variant: markdown_github
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

# kagari (縢り)

This package organizes individual data from various measuring instruments into tidy dataset.
`kagari` is a Japanese word meaning sew (c.f [和綴じ](https://www.google.co.jp/search?q=%E5%92%8C%E7%B6%B4%E3%81%98&source=lnms&tbm=isch)).
The author wish to sew a user-friendly book---i.e. tidy dataset---from individual pages---i.e. messy raw data.

You can install:

* the latest development version from github with

```R
# install.packages("devtools") # if not installed
devtools::install_github("KeachMurakami/kagari")
```

## Reading

`read_***` handles raw data obtained by `***`---a name of the software or the device:

* `read_field_lambda()`: read `.csv` format data obtained by color viewer for field-lambda.

* `read_junior_pam()`: read `.csv` format data obtained by WinControl for JUNIOR-PAM (Heinz Walz).

* `read_color_reader()`: read `.csv` format data obtained by CR-10 Plus (Konica Minolta).


The first argument is always a file path.  
The output is wide format data containing the measured variables and measured time.  

<!-- ```{r demo_read} -->
<!-- library(gasexchangeR) -->

<!-- sample_single <- "https://raw.githubusercontent.com/KeachMurakami/gasexchangeR/master/R/LI6400.txt" -->
<!-- sample_multi <- c("https://raw.githubusercontent.com/KeachMurakami/gasexchangeR/master/R/LI6400.txt", -->
<!--                   "https://raw.githubusercontent.com/KeachMurakami/gasexchangeR/master/R/LI6400XT.txt") -->

<!-- # simple read -->
<!-- read_licor(file = sample_single) -->

<!-- # include logs for changes in conditions -->
<!-- read_licor(file = sample_single, info_log = T) -->

<!-- # read multiple files into a data frame -->
<!-- read_licor(file = sample_multi) -->
<!-- ``` -->


<!-- ## Visualizations -->

<!-- `gasexchangeR` implements the following verbs useful for visualizations: -->

<!-- * `li_scat()`: view a relationship between variables -->
<!--     * `li_scat_light()`: -->
<!--     * `li_scat_co2()`: -->
<!--     * `li_scat_h2o()`: -->
<!--     * `li_scat_temp()`: -->
<!-- * `li_course()`: view time course of a variable -->
<!-- * `li_check()`: view primitive plots to check the environmental stability during the measurement -->

<!-- ```{r demo_plot} -->
<!-- li_scat(file = sample_multi, color = "VpdL") -->
<!-- li_course(file = sample_multi, color = "Ci") -->
<!-- ``` -->


## Session information

```{r sessioninfo}
devtools::session_info()
```
